---
title: "ESMR 2022 Multiverse Meta-Analysis"
subtitle: "3. Inferential Specification Curve Plot"
author: "Constantin Yves Plessen"
date: "`r format(Sys.time(), '%d %B, %Y')`"
knit: (function(inputFile, encoding) {
      rmarkdown::render(inputFile, 
      encoding = encoding, 
      output_dir = "html") })
output:
  html_document:
    code_folding: show
    highlight: pygment
    theme: cerulean
    toc: yes
    toc_depth: 2
    toc_float: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(metafor)
library(tidyverse) #data management

set.seed(1234)
options(scipen = 999)
```

The code is adapted from [this paper](https://doi.org/10.1027/2151-2604/a000357). 

<br>

# Scenario A: True Effect

## Load data 
```{r}
dat_boot <- read_csv2("data/data_sim.csv")
head(dat_boot)
```

<br>

```{r load-data-for-bootstrapping}
specifications_inferential_spec_curve <- read.csv2(file = "data/specifications_full.csv")
```

<br>

### Load unique specification study subsets found via the "Which" factors 
```{r load-unique-which-factor-combinations-bootstrapping}
sets <- as.vector(unique(specifications_inferential_spec_curve$set))
sets <- lapply(strsplit(sets, ","), as.numeric)
```

<br>

## Set up loop under null scenario

### Number of specifications (number of unique study subsets times number of How Factor Combinations)
```{r number-of-specifications-for-bootstrapping}
no_spec <- length(sets) * 4 # no RVE and puniform
```

<br>

### Number of iterations

This runs for a long time if you do 1000 iterations!

```{r}
iter <- 10 # 1000
```

<br>

### Matrix to save bootstrapped specification curves
```{r}
# Matrix to save bootstrapped specification curves
res <- matrix(numeric(iter * no_spec), ncol = iter)
```

### spec_list() function
```{r}
# Function that takes the ids of studies for each unique specification regarding the included studies (Which factors), 
# and computes the resulting summary effect for each of the 4 "How factors".
spec_list  <- function(ids, data) {
  temp <- data[ids, ]
  spec <- 
    c(rma(yi = yi,  # FE
          vi = vi, 
          method = "FE", 
          data = temp)$b[[1]],
      rma(yi = yi, # REML
          vi = vi, 
          method = "REML", 
          control = list(stepadj = 0.5, maxiter = 2000), 
          data = temp)$b[[1]],
      rma(yi = yi, # UW
          vi = vi, 
          method = "FE", 
          weights = 1/nrow(temp), 
          data = temp)$b[[1]],
      rma.mv(yi = yi, 
             V = vi, 
             method = "REML", 
             control=list(optimizer="optim", optmethod="Nelder-Mead"),
             random = list(~1 | es_id,
                           ~1 | study_name), 
             sparse=TRUE,
             data  = temp)$b[[1]]
    )
  spec
}
```

## Loop to draw specification curves under the null hypothesis iter times
```{r}
for(j in 1:iter) {
  # Draw randomly new effect sizes (Cohens d) from a normal distribution with SE = sqrt(sampling variance) 
  # and expectation 0 for each study in the data set
  dat_boot  <- dat_boot %>% 
    # ES of simulated data
    mutate(yi = rnorm(nrow(dat_boot), 
                        mean = 0, 
                        sd = sqrt((n1i + n2i)/(n1i*n2i) + 1/((2*(n1i + n2i))))),
           # vi of simulated data
           vi = (n1i + n2i)/(n1i*n2i) + 1/((2*(n1i + n2i))))
  # Store the sorted summary effects for each specification (i.e. the null specifaction curves)
  res[, j] <- sort(unlist(lapply(sets, FUN = function(x) spec_list(x, data = dat_boot))))
}

# Compute the 2.5% and 97.5% quantile of all specifiaction curves for each position as reference
boot_lb <- apply(res, 1, function(x) {quantile(x, probs = 0.025)})
boot_ub <- apply(res, 1, function(x) {quantile(x, probs = 0.975)})

# Save bootstrap upper and lower limits together with the observed specification curve
specifications_inferential_spec_curve <- specifications_inferential_spec_curve %>% 
  filter(ma_method %in% c("fe", "reml", "uw", "3-level"))

dat_boot <- data.frame(xvar = 1:no_spec, obs = sort(specifications_inferential_spec_curve$mean), boot_lb, boot_ub)
write.csv2(file = "data/inferential_data.csv", dat_boot)
```




## Plot
```{r}
boot_plot <- 
  ggplot(data = dat_boot, aes(x = xvar, y = obs)) +
  geom_ribbon(aes(x =  xvar, ymin = boot_lb, ymax = boot_ub*10),  # multiplication just to visualize this simulated example!!!
              fill = "gray", color = "black", lty = "dotted", alpha = 0.7, size = 0.25) +
  geom_line(col = "firebrick", size = 0.5) +
  geom_hline(yintercept = 0, linetype = 2, size = 0.25) +
  scale_x_continuous(name = "Specification number") +
  scale_y_continuous(name = "Summary effect") +
  ggtitle("Inferential Specification Curve") +
  coord_cartesian(xlim = c(0.5, nrow(dat_boot) + 0.5), expand = FALSE) +
  theme_bw() +
  theme(legend.position = "none")

boot_plot
```

<br>

### Save Plot
```{r}
ggsave("figures/boot_plot.png", 
       plot = boot_plot, 
       dpi = "retina",
       height = 7.5, 
       width = 10, 
       units = "cm")
```

<br>

# Scenario B: Null Effect

## Load data
```{r}
dat_boot_null <- read_csv2("data/data_sim_null.csv")
head(dat_boot_null)

specifications_inferential_spec_curve_null<- read.csv2(file = "data/specifications_full_null.csv")

head(specifications_inferential_spec_curve_null)
```

<br>

### Load unique specification study subsets found via the "Which" factors 
```{r  }
sets <- as.vector(unique(specifications_inferential_spec_curve_null$set))
sets <- lapply(strsplit(sets, ","), as.numeric)
```

<br>

## Set up loop under null scenario

### Number of specifications (number of unique study subsets times number of How Factor Combinations)
```{r  }
no_spec <- length(sets) * 4 # no RVE and puniform
```
<br>

### Number of iterations

This runs for a long time if you do 1000 iterations!
```{r}
iter <- 10 # 1000
```

<br>

### Matrix to save bootstrapped specification curves
```{r}
res <- matrix(numeric(iter * no_spec), ncol = iter)
```

<br>

## Loop to draw specification curves under the null hypothesis iter times

```{r}
for(j in 1:iter) {
  # Draw randomly new effect sizes (Cohens d) from a normal distribution with SE = sqrt(sampling variance)
  # and expectation 0 for each study in the data set
  dat_boot_null  <- dat_boot_null %>% 
    # ES of simulated data
    mutate(yi = rnorm(nrow(dat_boot_null), 
                        mean = 0, 
                        sd = sqrt((n1i + n2i)/(n1i*n2i) + 1/((2*(n1i + n2i))))),
           # vi of simulated data
           vi = (n1i + n2i)/(n1i*n2i) + 1/((2*(n1i + n2i))))
  # Store the sorted summary effects for each specification (i.e. the null specifaction curves)
  res[, j] <- sort(unlist(lapply(sets, FUN = function(x) spec_list(x, data = dat_boot_null))))
}

# Compute the 2.5% and 97.5% quantile of all specifiaction curves for each position as reference
boot_lb <- apply(res, 1, function(x) {quantile(x, probs = 0.025)})
boot_ub <- apply(res, 1, function(x) {quantile(x, probs = 0.975)})

# Save bootstrap upper and lower limits together with the observed specification curve
specifications_inferential_spec_curve_null <- specifications_inferential_spec_curve_null %>% 
  filter(ma_method %in% c("fe", "reml", "uw", "3-level"))

dat_boot_null <- data.frame(xvar = 1:no_spec, 
                            obs = sort(specifications_inferential_spec_curve_null$mean), 
                            boot_lb, boot_ub)
write.csv2(file = "data/inferential_data_null.csv", dat_boot_null)
```


## Plot
```{r}
boot_plot_null <- 
  ggplot(data = dat_boot_null, aes(x = xvar, y = obs)) +
  geom_ribbon(aes(x =  xvar, ymin = boot_lb , ymax = boot_ub), 
              fill = "gray", color = "black", lty = "dotted", alpha = 0.7, size = 0.25) +
  geom_line(col = "firebrick", size = 0.5) +
  geom_hline(yintercept = 0, linetype = 2, size = 0.25) +
  scale_x_continuous(name = "Specification number") +
  scale_y_continuous(name = "Summary effect") +
  ggtitle("Inferential Specification Curve") +
  coord_cartesian(xlim = c(0.5, nrow(dat_boot_null) + 0.5), expand = FALSE) +
  theme_bw() +
  theme(legend.position = "none")

boot_plot_null
```


### Save Plot
```{r}
ggsave("figures/boot_plot-null.pdf", 
       plot = boot_plot_null, 
       dpi = "retina",
       height = 7.5, 
       width = 10, 
       units = "cm")
```