---
title: "ESMR 2022 Multiverse Meta-Analysis"
subtitle: "1. Data Preperation"
author: "Constantin Yves Plessen"
date: "`r format(Sys.time(), '%d %B, %Y')`"
knit: (function(inputFile, encoding) {
      rmarkdown::render(inputFile, 
      encoding = encoding, 
      output_dir = "html") })
output:
  html_document:
    code_folding: show
    highlight: pygment
    theme: cerulean
    toc: yes
    toc_depth: 2
    toc_float: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse) # data cleaning
library(metafor)   # calculate meta-analytical models
library(puniform)  # calculate p-uniform*
set.seed(42)       # set seed for simulating studies
```

The code is adapted from [this paper](https://doi.org/10.1027/2151-2604/a000357). 

<br>

# Scenario A: True Effect ~ *g* = 0.8

## Simulate Data 

I simulate a scenario with a true difference between 2 groups, which will be represented as Hedges g. To be able to show systematic patterns for several which factors, I introduce some systematic differences:
- females will show larger differences
- therapy A will show larger differences
- therapy = "C" and non adults show even larger differences
- and there will be some random outliers

### Female data set
```{r}
data_female <- tibble( # I 
  es_id = 1:20, # unique effect size ids
  study_name = c(paste("Study", 1:10), paste("Study", sort(rep(11:15, 2))))) %>% # unique study id
  rowwise() %>%
  mutate(m1i = rnorm(1, mean = 10, sd = 0.5),
         m2i = rnorm(1, mean = 8, sd = 0.5),
         sd1i = rnorm(1, mean = 2, sd = 0.5),
         sd_2 = rnorm(1, mean = 2, sd = 0.5),
         n1i = sample(10:100, 1),
         n2i = n1i,
         n =n1i + n2i,
         
         # WHICH FACTORS
         age_group = sample(c("adults", "non-adults"), 1), # age should be random for this example
         sex = "female",
         therapy = "A")
```


### Male data set
```{r}
data_male <- tibble(
  es_id = 21:40,
  study_name = c(paste("Study", 16:25), paste("Study", sort(rep(26:30, 2))))) %>% 
  rowwise() %>%
  mutate(m1i = rnorm(1, mean = 10, sd = 0.5), 
         m2i = rnorm(1, mean = 9, sd = 0.5),
         sd1i = rnorm(1, mean = 2, sd = 0.5),
         sd_2 = rnorm(1, mean = 2, sd = 0.5),
         n1i = sample(10:100, 1),
         n2i = n1i,
         n = n1i + n2i,
         
         # WHICH FACTORS
         age_group = sample(c("adults", "non-adults"), 1),
         sex = "male",
         therapy = "B")
```

### Therapy = "C" and non adults show even larger differneces
```{r}
data_similar <- tibble(
  es_id = 41:60,
  study_name = c(paste("Study", 31:40), paste("Study", sort(rep(41:45, 2))))) %>% 
  rowwise() %>%
  mutate(m1i = rnorm(1, mean = 10, sd = 0.5), 
         m2i = rnorm(1, mean = 7, sd = 0.5),
         sd1i = rnorm(1, mean = 2, sd = 0.5),
         sd_2 = rnorm(1, mean = 2, sd = 0.5),
         n1i = sample(10:100, 1),
         n2i = n1i,
         n = n1i + n2i,
         
         # WHICH FACTORS
         age_group = "non-adults",
         sex = sample(c("male", "female"), 1),
         therapy = "C")
```

### And we have some very strong outliers 
```{r}
data_outlier <- tibble(
  es_id = 61:65,
  study_name = c(paste("Study",46:50))) %>% 
  rowwise() %>%
  mutate(m1i = rnorm(1, mean = 10, sd = .22), 
         m2i = rnorm(1, mean = 7, sd = .22),
         sd1i = rnorm(1, mean = 1, sd = 0.1),
         sd_2 = rnorm(1, mean = 1, sd = 0.1),
         n1i = sample(10:100, 1),
         n2i = n1i,
         n =n1i + n2i,
         
         # WHICH FACTORS
         age_group = sample(c("adults", "non-adults"), 1),
         sex = sample(c("male", "female"), 1),
         therapy = sample(c("A", "B"), 1))
```

### Binding data sets
```{r}
data_sim <- bind_rows(data_female, data_male, data_similar, data_outlier)
```


### Calculating Hedges *g*

```{r}
data_sim <- escalc(measure = "SMD", 
                   data = data_sim, # calculate  Hedges g = yi, variance of g = vi, and se
                   m1i = m1i,
                   sd1i = sd1i,
                   n1i = n1i,
                   m2i = m2i,
                   sd2i = sd_2,
                   n2i = n2i) %>% 
  data.frame(.)
```

<br>

### Create Outlier Variable

Here I create an outlier variable, that could also include different cutoffs, for example: d-poop, which I personally find both hilarious and reasonable. 
I base this on  DOI: 10.1177/0956797609356283: 
> "In a pretest, we confirmed that chocolates were more desirable than feces. A separate group of participants (n = 20) rated how appealing, positive, likeable, attractive, and interesting both objects were. It should come as no surprise that averages across these qualities indicated that the chocolates (M = 5.5) were more desirable than the feces (M = 2.1), paired t(19) = 17.44, prep = .99, p < .001, d = 4.52."

Any effect size larger than this seems unreasonable to me and must be an outlier. It just must.

```{r}
data_sim <- data_sim %>% 
  cbind(ci_lower, ci_upper) %>% 
  relocate(study_name, yi, ci_lower, ci_upper) %>% 
  mutate(outlier = case_when(
    yi > 3 ~ "ES > 3",
    TRUE ~ "ES > 3 removed",
      )) 
```

<br>

### Save Data set

```{r}
write.csv2(file = "data/data_sim.csv", 
           data_sim)
```

<br>

## Specification Curve

All Which and How factors need to be specified in this order. 

### Which factors
```{r}
age_group     <- c(unique(data_sim$age_group), "all groups")
sex      <- c(unique(data_sim$sex), "all sexes")
therapy  <- c(unique(data_sim$therapy), "all therapy")
outlier       <- c("ES > 3 removed", "all es")
```


### How Factors
```{r}
ma_method     <- c("3-level", "rve", "reml", "fe", "uw", "p-uniform")
```


### Construct all specifications
```{r}
specifications_grid <- expand.grid(
  age_group = age_group,
  sex = sex,
  therapy = therapy,
  outlier = outlier,
  ma_method = ma_method)
head(specifications_grid)

number_specs <- nrow(specifications_grid)
number_specs
```

<br>

### Empty specifications frame to save means, CI, p values and k

```{r }
specifications <- data.frame(specifications_grid, 
                             mean = rep(NA, nrow(specifications_grid)), 
                             lb = rep(NA, nrow(specifications_grid)), 
                             ub = rep(NA, nrow(specifications_grid)), 
                             p = rep(NA, nrow(specifications_grid)), 
                             k = rep(NA, nrow(specifications_grid)))
head(specifications)
```

<br>

### Giant for loop aka the specification analyis aka the multiverse meta-analysis

```{r}
for(i in 1:nrow(specifications)) {
  
  dat <- as.data.frame(data_sim)
  
  # Determine specification subsets by using "Which" factors 
  
  # age_group 
  if(specifications$age_group[i] == "adults") {
    dat <- dat[dat$age_group == "adults", ] 
  } else {
    if(specifications$age_group[i] == "non-adults") {
      dat <- dat[dat$age_group == "non-adults", ] 
    }
  }
  
  # sex  
  if(specifications$sex[i] == "female") {
    dat <- dat[dat$sex == "female", ] 
  } else {
    if(specifications$sex[i] == "male") {
      dat <- dat[dat$sex == "male", ] 
    }
  }
  
  # rob
  if(specifications$therapy[i] == "A") {
    dat <- dat[dat$therapy == "A", ] 
  } else {
    if(specifications$therapy[i] == "B") {
      dat <- dat[dat$therapy == "B", ] 
    } else {
      if(specifications$therapy[i] == "C") {
        dat <- dat[dat$therapy == "C", ] 
      }
    }
  }
  
  # outlier 
  if(specifications$outlier[i] == "ES > 3 removed") {
    dat <- dat[dat$outlier == "ES > 3 removed", ] 
  }
  
  
  # only compute meta-analytic summary effects for specification subsets with at least 2 studies/samples.
  if(nrow(dat) < 2) next
  
  # Save which study/sample IDs were selected by the "Which" factors for a given specification.
  specifications$set[i] <- paste(rownames(dat), collapse = ",")
  
  if(specifications$ma_method[i] == "3-level" | specifications$ma_method[i] == "rve" & sum(duplicated(dat$study_name)) > 0) { # nested effect sizes detected) if more duplicated study id
    mod1 <- rma.mv(data = dat, 
                   yi = yi, 
                   V = vi, 
                   method = "REML", 
                   control=list(optimizer="optim", optmethod="Nelder-Mead"),
                   random = list(~1 | es_id,
                                 ~1 | study_name), 
                   sparse=TRUE)
    
    if(specifications$ma_method[i] == "3-level") mod <- mod1
    
    if(specifications$ma_method[i] == "rve") mod <- robust(mod1, cluster=dat$study, clubSandwich=TRUE)
    
    
  } else {
    if(specifications$ma_method[i] == "reml" & sum(duplicated(dat$study_name)) > 0) { 
      # average data in case of nested structure
      
      dat <- dat %>% 
        select(study_name, age_group, sex, therapy, outlier, yi, vi) %>% 
        escalc(yi=yi, vi=vi, data=.)
      dat <- as.data.frame(aggregate(dat, cluster = study_name, struct="ID"))
      mod <- rma(yi = dat$yi, vi = dat$vi, 
                 method = "REML", 
                 control = list(stepadj = 0.5,
                                maxiter = 2000))  
      
    } else {
      if(specifications$ma_method[i] == "reml" & sum(duplicated(dat$study_name)) == 0) {
        mod <- rma(yi = dat$yi, vi = dat$vi, 
                   method = "REML", 
                   control = list(stepadj = 0.5,
                                  maxiter = 2000))  
        
      } else {
        if(specifications$ma_method[i] == "fe") {
          dat <- dat %>% 
            select(study_name, age_group, sex, therapy, outlier, yi, vi) %>% 
            escalc(yi=yi, vi=vi, data=.)
          dat <- as.data.frame(aggregate(dat, cluster = study_name, struct="ID"))
          mod <- rma(yi = dat$yi, vi = dat$vi, 
                     method = "FE")  
        } else {
          if(specifications$ma_method[i] == "uw") {
            dat <- dat %>% 
              select(study_name, age_group, sex, therapy, outlier, yi, vi) %>% 
              escalc(yi=yi, vi=vi, data=.)
            dat <- as.data.frame(aggregate(dat, cluster = study_name, struct="ID"))
            mod <- rma(yi = dat$yi, vi = dat$vi,
                       method = "FE", 
                       weights = 1/nrow(dat))
          } else {
            if(specifications$ma_method[i] == "p-uniform") {
              dat <- dat %>% 
                select(study_name, age_group, sex, therapy, outlier, yi, vi) %>% 
                escalc(yi=yi, vi=vi, data=.)
              dat <- as.data.frame(aggregate(dat, cluster = study_name, struct="ID"))
              mod <- puni_star(yi = dat$yi, vi = dat$vi, 
                               side = "right")
              mod$b <- mod$est
              mod$pval <- mod$pval.0 
            }
          }
        }
      }
    }
  }
  specifications$mean[i] <- mod$b[[1]]
  specifications$lb[i] <- mod$ci.lb[[1]]
  specifications$ub[i] <- mod$ci.ub[[1]]
  specifications$p[i] <- mod$pval[[1]]
  specifications$k[i] <- nrow(dat)
}
```

```{r}
specifications
```

<br>

## Cleaning specifications

### Only keep specifications with at least 2 studies/samples

```{r clean-specifications-minimum-2-studies}
specifications_full <- specifications[complete.cases(specifications),]
```

<br>

### Only keep unique study/sample subsets resulting from "Which" factor combinations.

```{r clean-specifications-keep-unique-sets}
specifications_full <- specifications_full[!duplicated(specifications_full[, c("mean", "set", "ma_method")]), ]
```

<br>

### Indicator if all studies are included in the set

```{r clean-specifications-add-indicator}
specifications_full$full_set <- as.numeric(specifications_full$set == paste(1:nrow(data_sim), collapse =",", sep = ""))
```

<br>

## Descriptives of specifications

<br>

### Overall

```{r}
specifications_full %>% 
  dplyr::summarise(mean_g = mean(mean),
                   max = max(mean),
                   min = min(mean),
                   mean_lb = mean(lb),
                   mean_ub = mean(ub),
                   n =n()) %>% 
  mutate(set = "full")
```

<br>

### Age Group

```{r}
specifications_full %>% 
  group_by(age_group) %>% 
  dplyr::summarise(mean_g = mean(mean),
                   max = max(mean),
                   min = min(mean),
                   lb = mean(lb),
                   ub = mean(ub),
                   n =n())
```


<br>

### sex
```{r}
specifications_full %>% 
  group_by(sex) %>% 
  dplyr::summarise(mean_g = mean(mean),
                   max = max(mean),
                   min = min(mean),
                   lb = mean(lb),
                   ub = mean(ub),
                   n =n())
```

<br>


### outlier
```{r}
specifications_full %>% 
  group_by(outlier) %>% 
  dplyr::summarise(mean_g = mean(mean),
                   max = max(mean),
                   min = min(mean),
                   lb = mean(lb),
                   ub = mean(ub),
                   n =n())
```


```{r}
specifications_full %>% 
  group_by(therapy) %>% 
  dplyr::summarise(mean_g = mean(mean),
                   max = max(mean),
                   min = min(mean),
                   lb = mean(lb),
                   ub = mean(ub),
                   n =n())
```
<br>

### ma_method
```{r}
specifications_full %>% 
  group_by(ma_method) %>% 
  dplyr::summarise(mean_g = mean(mean),
                   max_g = max(mean),
                   min_g = min(mean),
                   lb = mean(lb),
                   ub = mean(ub),
                   n =n())
```

<br>

### k
```{r}
specifications_full %>% 
  ggplot(aes(x = k)) + 
  geom_histogram(bins = 30) +
  theme_classic()
```

<br>

## Saving Specifications
```{r}
write.csv2(file = "data/specifications_full.csv", 
           specifications_full)
```

<br>

# Scenario B: True Effect ~ *g* = 0.0

## Simulate Data

I simulate a data set as above, but with no a null effect and some outliers
```{r}
data_female <- tibble( # I 
  es_id = 1:20, # unique effect size ids
  study_name = c(paste("Study", 1:10), paste("Study", sort(rep(11:15, 2))))) %>% # unique study id
  rowwise() %>%
  mutate(m1i = rnorm(1, mean = 10, sd = 2),
         m2i = rnorm(1, mean = 10, sd = 2),
         sd1i = rnorm(1, mean = 2, sd = 0.5),
         sd_2 = rnorm(1, mean = 2, sd = 0.5),
         n1i = sample(10:100, 1),
         n2i = n1i,
         
         n =n1i + n2i,
         age_group = sample(c("adults", "non-adults"), 1), # age should be random for this example
         sex = "female",
         therapy = "A")

data_male <- tibble(
  es_id = 21:40,
  study_name = c(paste("Study", 16:25), paste("Study", sort(rep(26:30, 2))))) %>% 
  rowwise() %>%
  mutate(m1i = rnorm(1, mean = 10, sd = 2), 
         m2i = rnorm(1, mean = 10, sd = 2),
         sd1i = rnorm(1, mean = 2, sd = 0.5),
         sd_2 = rnorm(1, mean = 2, sd = 0.5),
         n1i = sample(10:100, 1),
         n2i = n1i,
         
         n =n1i + n2i,
         age_group = sample(c("adults", "non-adults"), 1),
         sex = "male",
         therapy = "A")

data_similar<- tibble(
  es_id = 41:60,
  study_name = c(paste("Study", 31:40), paste("Study", sort(rep(41:45, 2))))) %>% 
  rowwise() %>%
  mutate(m1i = rnorm(1, mean = 10, sd = 2), 
         m2i = rnorm(1, mean = 10, sd = 2),
         sd1i = rnorm(1, mean = 2, sd = 0.5),
         sd_2 = rnorm(1, mean = 2, sd = 0.5),
         n1i = sample(10:100, 1),
         n2i = n1i,
         n =n1i + n2i,
         age_group = sample(c("adults", "non-adults"), 1),
         sex = "male",
         therapy = "B")

data_male_outlier <- tibble(
  es_id = 61:65,
  study_name = c(paste("Study",46:50))) %>% 
  rowwise() %>%
  mutate(m1i = rnorm(1, mean = 10, sd = .22), 
         m2i = rnorm(1, mean = 9, sd = .22),
         sd1i = rnorm(1, mean = 1, sd = 0.1),
         sd_2 = rnorm(1, mean = 1, sd = 0.1),
         n1i = sample(10:100, 1),
         n2i = n1i,
         
         n =n1i + n2i,
         age_group = sample(c("adults", "non-adults"), 1),
         sex = "male",
         therapy = "C")

data_sim_null <- bind_rows(data_female, data_male, data_similar ,data_male_outlier)
```

#### Calculate Hedges *g*

```{r}
data_sim_null <- escalc(measure = "SMD", 
                   data = data_sim_null, # calculate  Hedges g = yi, variance of g = vi, and se
                   m1i = m1i,
                   sd1i = sd1i,
                   n1i = n1i,
                   m2i = m2i,
                   sd2i = sd_2,
                   n2i = n2i) %>% 
  data.frame(.)
```

<br>

### Create Outlier Variable

```{r}
data_sim_null <- data_sim_null %>% 
  cbind(ci_lower, ci_upper) %>% 
  relocate(study_name, yi, ci_lower, ci_upper) %>% 
  mutate(outlier = case_when(
    yi > 3 ~ "ES > 3",
    TRUE ~ "ES > 3 removed",    # contains the studies that are below the cutoff, and should be included as"ES > 3 removed" Which factor
      )) 
```

<br>

### Save Data set

```{r}
write.csv2(file = "data/data_sim_null.csv", 
           data_sim_null)
```

<br>

## Specification Curve

### Define all which and how factors

```{r}
age_group     <- c(unique(data_sim_null$age_group), "all groups")
sex      <- c(unique(data_sim_null$sex), "all sexes")
therapy  <- c(unique(data_sim_null$therapy), "all therapy")
outlier       <- c("ES > 3 removed", "all es")
ma_method     <- c("3-level", "rve", "reml", "fe", "uw", "p-uniform")
```

```{r}
specifications_grid <- expand.grid(
  age_group = age_group,
  sex = sex,
  therapy = therapy,
  outlier = outlier,
  ma_method = ma_method)
head(specifications_grid)

number_specs <- nrow(specifications_grid)
number_specs
```

<br>

### Empty specifications frame to save means, CI, p values and k

```{r }
specifications <- data.frame(specifications_grid, 
                             mean = rep(NA, nrow(specifications_grid)), 
                             lb = rep(NA, nrow(specifications_grid)), 
                             ub = rep(NA, nrow(specifications_grid)), 
                             p = rep(NA, nrow(specifications_grid)), 
                             k = rep(NA, nrow(specifications_grid)))
head(specifications)
```

### Giant for loop

```{r}
for(i in 1:nrow(specifications)) {
  
  dat <- as.data.frame(data_sim_null)
  
  # Determine specification subsets by using "Which" factors 
  
  # age_group 
  if(specifications$age_group[i] == "adults") {
    dat <- dat[dat$age_group == "adults", ] 
  } else {
    if(specifications$age_group[i] == "non-adults") {
      dat <- dat[dat$age_group == "non-adults", ] 
    }
  }
  
  # sex  
  if(specifications$sex[i] == "female") {
    dat <- dat[dat$sex == "female", ] 
  } else {
    if(specifications$sex[i] == "male") {
      dat <- dat[dat$sex == "male", ] 
    }
  }
  
  # rob
  if(specifications$therapy[i] == "A") {
    dat <- dat[dat$therapy == "A", ] 
  } else {
    if(specifications$therapy[i] == "B") {
      dat <- dat[dat$therapy == "B", ] 
    } else {
      if(specifications$therapy[i] == "C") {
        dat <- dat[dat$therapy == "C", ] 
      }
    }
  }
  
  # outlier 
  if(specifications$outlier[i] == "ES > 3 removed") {
    dat <- dat[dat$outlier == "ES > 3 removed", ] 
  }
  
  
  # only compute meta-analytic summary effects for specification subsets with at least 2 studies/samples.
  if(nrow(dat) < 2) next
  
  # Save which study/sample IDs were selected by the "Which" factors for a given specification.
  specifications$set[i] <- paste(rownames(dat), collapse = ",")
  
  if(specifications$ma_method[i] == "3-level" | specifications$ma_method[i] == "rve" & sum(duplicated(dat$study_name)) > 0) { # nested effect sizes detected) if more duplicated study id
    mod1 <- rma.mv(data = dat, 
                   yi = yi, 
                   V = vi, 
                   method = "REML", 
                   control=list(optimizer="optim", optmethod="Nelder-Mead"),
                   random = list(~1 | es_id,
                                 ~1 | study_name), 
                   sparse=TRUE)
    
    if(specifications$ma_method[i] == "3-level") mod <- mod1
    
    if(specifications$ma_method[i] == "rve") mod <- robust(mod1, cluster=dat$study, clubSandwich=TRUE)
    
    
  } else {
    if(specifications$ma_method[i] == "reml" & sum(duplicated(dat$study_name)) > 0) { 
      # average data in case of nested structure
      
      dat <- dat %>% 
        select(study_name, age_group, sex, therapy, outlier, yi, vi) %>% 
        escalc(yi=yi, vi=vi, data=.)
      dat <- as.data.frame(aggregate(dat, cluster = study_name, struct="ID"))
      mod <- rma(yi = dat$yi, vi = dat$vi, 
                 method = "REML", 
                 control = list(stepadj = 0.5,
                                maxiter = 2000))  
      
    } else {
      if(specifications$ma_method[i] == "reml" & sum(duplicated(dat$study_name)) == 0) {
        mod <- rma(yi = dat$yi, vi = dat$vi, 
                   method = "REML", 
                   control = list(stepadj = 0.5,
                                  maxiter = 2000))  
        
      } else {
        if(specifications$ma_method[i] == "fe") {
          dat <- dat %>% 
            select(study_name, age_group, sex, therapy, outlier, yi, vi) %>% 
            escalc(yi=yi, vi=vi, data=.)
          dat <- as.data.frame(aggregate(dat, cluster = study_name, struct="ID"))
          mod <- rma(yi = dat$yi, vi = dat$vi, 
                     method = "FE")  
        } else {
          if(specifications$ma_method[i] == "uw") {
            dat <- dat %>% 
              select(study_name, age_group, sex, therapy, outlier, yi, vi) %>% 
              escalc(yi=yi, vi=vi, data=.)
            dat <- as.data.frame(aggregate(dat, cluster = study_name, struct="ID"))
            mod <- rma(yi = dat$yi, vi = dat$vi,
                       method = "FE", 
                       weights = 1/nrow(dat))
          } else {
            if(specifications$ma_method[i] == "p-uniform") {
              dat <- dat %>% 
                select(study_name, age_group, sex, therapy, outlier, yi, vi) %>% 
                escalc(yi=yi, vi=vi, data=.)
              dat <- as.data.frame(aggregate(dat, cluster = study_name, struct="ID"))
              mod <- puni_star(yi = dat$yi, vi = dat$vi, 
                               side = "right")
              mod$b <- mod$est
              mod$pval <- mod$pval.0 
            }
          }
        }
      }
    }
  }
  specifications$mean[i] <- mod$b[[1]]
  specifications$lb[i] <- mod$ci.lb[[1]]
  specifications$ub[i] <- mod$ci.ub[[1]]
  specifications$p[i] <- mod$pval[[1]]
  specifications$k[i] <- nrow(dat)
}
```

```{r}
specifications
```

<br>

## Cleaning specifications

### Only keep specifications with at least 2 studies/samples

```{r}
specifications_full <- specifications[complete.cases(specifications),]
```

<br>

### Only keep unique study/sample subsets resulting from "Which" factor combinations.

```{r }
specifications_full <- specifications_full[!duplicated(specifications_full[, c("mean", "set", "ma_method")]), ]
```

<br>

### Indicator if all studies are included in the set

```{r }
specifications_full$full_set <- as.numeric(specifications_full$set == paste(1:nrow(data_sim_null), collapse =",", sep = ""))
```

<br>

## Descriptives of specifications

<br>

### Overall

```{r}
specifications_full %>% 
  dplyr::summarise(mean_g = mean(mean),
                   max = max(mean),
                   min = min(mean),
                   mean_lb = mean(lb),
                   mean_ub = mean(ub),
                   n =n()) %>% 
  mutate(set = "full")
```

<br>

### Age Group

```{r}
specifications_full %>% 
  group_by(age_group) %>% 
  dplyr::summarise(mean_g = mean(mean),
                   max = max(mean),
                   min = min(mean),
                   lb = mean(lb),
                   ub = mean(ub),
                   n =n())
```


<br>
### sex
```{r}
specifications_full %>% 
  group_by(sex) %>% 
  dplyr::summarise(mean_g = mean(mean),
                   max = max(mean),
                   min = min(mean),
                   lb = mean(lb),
                   ub = mean(ub),
                   n =n())
```

<br>


### outlier
```{r}
specifications_full %>% 
  group_by(outlier) %>% 
  dplyr::summarise(mean_g = mean(mean),
                   max = max(mean),
                   min = min(mean),
                   lb = mean(lb),
                   ub = mean(ub),
                   n =n())
```


```{r}
specifications_full %>% 
  group_by(therapy) %>% 
  dplyr::summarise(mean_g = mean(mean),
                   max = max(mean),
                   min = min(mean),
                   lb = mean(lb),
                   ub = mean(ub),
                   n =n())
```
<br>

### ma_method
```{r}
specifications_full %>% 
  group_by(ma_method) %>% 
  dplyr::summarise(mean_g = mean(mean),
                   max_g = max(mean),
                   min_g = min(mean),
                   lb = mean(lb),
                   ub = mean(ub),
                   n =n())
```

<br>

### k
```{r}
specifications_full %>% 
  ggplot(aes(x = k)) + 
  geom_histogram(bins = 30) +
  theme_classic()
```

<br>

## Saving Specifications
```{r}
write.csv2(file = "data/specifications_full_null.csv", 
           specifications_full)
```

